Cosmmus? Suporte a jogos maciçamente multijogador em cenários com recursos limitados

### 2009-03-27 trunk/disciplinas/cmp112/artigo1/blindengaoi.tex

There is another question, concerning the number of transmissions that each peer needs to execute. In the client-server model, each player only needs to send his actions to the server, which processes them and broadcasts the resulting game state to every player. In the peer-to-peer model, each peer becomes responsible for processing its own player's actions and send the resulting state to everyone else to whom that state change is relevant. The problem is that we cannot assume that every peer has enough bandwidth to do this. Besides, without a central server, the game becomes dependent on the peers' simulation, which may be corrupted in order to result in an invalid state that benefits a player, or even invalidate the whole game session.

@@

One issue that relates to that type of partitioning of the virtual environment concerns the borders between regions. If an avatar is close to the border between two regions, it will be necessary some exchange of information between the servers which manage them. This information consists of state updates of the entities that are interacting with each other despite being located in different regions. Such situations imply a higher bandwidth usage, as it is also required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of the simulation identical among all of them. Furthermore, the hop count of each message between the clients will be increased, since there are two intermediary servers between them.

@@

Before sending the state of an entity to a client, the last transmission time is checked. The next transmission is then scheduled to occur after a certain interval. If the relevance of that state is 1, the normal update interval will be used. If it is less than 1, the normal interval is divided by the relevance. For example, let the normal update interval of a game be \mbox{200 ms}. Also, let $A_i$ be the avatar of a player who just received a state update packet from $A_j$. If $A_j$ is at a distance from $A_i$ such that its relevance is 0.5, the next transmission will only happen after an interval of 200 divided by 0.5. So, the player controlling $A_i$ will only receive another update from $A_j$ after 400 ms. Despite this interval is still less than a half second, it represents a reduction of the state update frequency of $A_j$ in 50\%, to the player of $A_i$. As they are at a greater distance from one another, and the interval was increased only by 200 ms, this variation will probably be imperceptible by the player.

@@

\begin{itemize}
 \item Normal update interval: 250 ms;
 \item State update for one entity: 100 bytes UDP packet;
 \item Duration of each simulated game session: 20 min;
 \item Virtual environment area: 750 x 750;
 \item View distance: 120;
 \item Critical distance: 40;
 \item View angle: 180°.
\end{itemize}

>>>>

There is another question, concerning the number of transmissions that each peer needs to execute. In the client-server model, each player only needs to send his actions to the server, which processes them and broadcasts the resulting game state to the other players. In the peer-to-peer model, each peer becomes responsible for processing its own player's actions and send the resulting state to everyone else to whom that state change is relevant. The problem is that we cannot assume that every peer has enough bandwidth to do this. Besides, without a central server, the game becomes dependent on the peers' simulation, which may be corrupted in order to result in an invalid state that benefits a player, or even invalidate the whole game session.

@@

One issue that relates to that type of partitioning of the virtual environment concerns the borders between regions. If an avatar is close to the border between two regions, it will be necessary some exchange of information between the servers which manage them. This information consists of state updates of the entities that are interacting with each other despite being located in different regions. Such situations imply a higher bandwidth usage, as it is also required some sort of negotiation between the servers to which the different players are connected, in order to maintain the states of the simulation identical among all of them. Furthermore, the hop count of each message between the clients will be increased, since there will be two intermediary servers.

@@

Before sending the state of an entity to a client, the last transmission time is checked. The next transmission is then scheduled to occur after a certain interval. If the relevance of that state is 1, the normal update interval will be used. If it is less than 1, the normal interval is divided by the relevance. For example, let the normal update interval of a game be \mbox{200 ms}. Also, let $A_i$ be the avatar of a player who just received a state update packet from $A_j$. If $A_j$ is at a distance from $A_i$ such that its relevance is 0.5, the next transmission will only happen after an interval of 200 divided by 0.5. Therefore, the player controlling $A_i$ will only receive another update from $A_j$ after 400 ms. Despite this interval is still less than a half second, it represents a reduction of the state update frequency of $A_j$ in 50\%, to the player of $A_i$. As they are at a greater distance from one another, and the interval was increased only by 200 ms, this variation will probably be imperceptible by the player.

@@

\begin{itemize}
 \item Normal update interval: 250 ms;
 \item State update for one entity: 100 bytes UDP packet;
 \item Duration of each simulated game session: 20 min;
 \item Virtual environment area: 750 $\times$ 750 area units;
 \item View distance: 120 length units;
 \item Critical distance: 40 length units;
 \item View angle: 180°.
\end{itemize}

### 2009-03-27 trunk/disciplinas/cmp112/artigo1/dsrt.tex

\begin{abstract}
%\boldmath
Traditionally, a central server is utilized %, to which players connect,
to provide support to massively multiplayer games, where the number of participants is of the order of tens of thousands. In this work, it is proposed the utilization of geographically distributed lower-cost nodes, employing techniques to minimize the necessary bandwidth to these server nodes. One of these techniques is a refinement of interest management algorithm, which obtained significant results in simulations. Other techniques still in preliminary phase of specification are: server nodes overlay network construction using knowledge of the real network topology, load balancing and hotspots dectection.

>>>>

\begin{abstract}
%\boldmath
Traditionally, a central server is utilized to provide support to massively multiplayer games, where the number of participants is of the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, but critical questions remain. Examples are: vulnerability to cheating, overload of the upload links of the peers and  In this work, it is proposed the utilization of geographically distributed lower-cost nodes, employing a novell refinement to the area of interest technique, which minimizes the necessary bandwidth to these server nodes.
